Deriving Multi-headed Planar Dependency Parses from Link Grammar Parses

### 2014-05-20 doc/LinksToDAG.tex
added notes from our meeting

@@

@@

>>>>

\NoteJE{discuss multiheadedness.  cite Kromann 2003's danish
  dependency treebank.  Prior work: McDonald and Pereira 2006, Sagae
  and Tsujii 2008, Gomez-Rodriguez and Nivre 2013.}
% http://aclweb.org/anthology/J/J13/J13-4002.pdf
% http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.156.3938&rep=rep1&type=pdf

@@

\TODO{more in the appendix ...}

@@

\appendix
\section{English Link Types}

\TODO{A table here that lists each link grammar type together with its
  count, its allowed direction(s), its percentage of majority
  directions by token, and its most common corresponding CoNLL tags
  with percentages.  Readers could cut-and-paste this data to make a 
  cheap post-processor for LG parses.}

\section{Sample English Parses}

\TODO{Show a bunch of English sentences with CoNLL vs.\@ link parses.
  Explain how they were selected and how the results are colorized etc.}
